### 2021-02-11 end_appendix/appendix.tex
Finished section 5.2

\begin{table}[!b]
  \centering
  \begin{tabulary}{\columnwidth}{L L L}
    \toprule
    Observational dataset & Corresponding variables & Reference \\
    \midrule
    AIRS & \emph{hur}, \emph{hus} & \textcite{Aumann2003} \\
    AMSRE SST & \emph{tos} & \textcite{AMSRE2011} \\
    CERES-EBAF & \emph{rsdt}, \emph{rsut}, \emph{rsutcs} & \textcite{Loeb2018}
    \\
    CloudSat/CALIPSO & \emph{cl} & \textcite{Mace2009} \\
    ERA-Interim & \emph{hur}, \emph{ta}, \emph{va}, \emph{wap} &
    \textcite{Dee2011} \\
    GPCP & \emph{pr} & \textcite{Adler2003} \\
    HadCRUT4 & \emph{tas} & \textcite{Morice2012} \\
    HadISST & \emph{ts} & \textcite{Rayner2003} \\
    ISCCP D-2 & \emph{clt} & \textcite{Rossow1991} \\
    MLS-Aura & \emph{hur} & \textcite{Beer2006} \\
    \bottomrule
  \end{tabulary}
  \caption{References for all observational datasets used in
    \cref{ch:05:paper_ecs} (\nameref*{ch:05:paper_ecs}).}
  \label{tab:app:a:observations}
\end{table}

>>>>

\begin{table}[!b]
  \centering
  \begin{tabulary}{\columnwidth}{L L L}
    \toprule
    Observational dataset & Corresponding variables & Reference \\
    \midrule
    AIRS & \emph{hur}, \emph{hus} & \textcite{Aumann2003} \\
    AMSRE \ac{SST} & \emph{tos} & \textcite{AMSRE2011} \\
    CERES-EBAF & \emph{rsdt}, \emph{rsut}, \emph{rsutcs} & \textcite{Loeb2018}
    \\
    Cloudsat/CALIPSO & \emph{cl} & \textcite{Mace2009} \\
    ERA-Interim & \emph{hur}, \emph{ta}, \emph{va}, \emph{wap} &
    \textcite{Dee2011} \\
    GPCP & \emph{pr} & \textcite{Adler2003} \\
    HadCRUT4 & \emph{tas} & \textcite{Morice2012} \\
    HadISST & \emph{ts} & \textcite{Rayner2003} \\
    ISCCP D-2 & \emph{clt} & \textcite{Rossow1991} \\
    MLS-Aura & \emph{hur} & \textcite{Beer2006} \\
    \bottomrule
  \end{tabulary}
  \caption{References for all observational datasets used in
    \cref{ch:05:paper_ecs} (\nameref*{ch:05:paper_ecs}).}
  \label{tab:app:a:observations}
\end{table}
